\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}


\title{The Economics of Cybersecurity: Homework 6}
\date{Due: April 9 at {\bf 5:00pm}}
\author{}

\begin{document}

\maketitle


\section{}

Read the following documents:

\begin{itemize}
    \item \href{https://nvlpubs.nist.gov/nistpubs/CSWP/NIST.CSWP.29.pdf}{The NIST Cybersecurity Framework} (pages 1--14, and skim the appendices)
    \item \href{https://www.whitehouse.gov/briefing-room/statements-releases/2023/03/02/fact-sheet-biden-harris-administration-announces-national-cybersecurity-strategy/}{National Cybersecurity Strategy Press Release}, plus skim the \href{https://www.whitehouse.gov/wp-content/uploads/2023/03/National-Cybersecurity-Strategy-2023.pdf}{document itself}
    \item \href{https://digital-strategy.ec.europa.eu/en/library/cyber-resilience-act}{EU Cyber Resilience Act Press Release} plus the \href{https://eur-lex.europa.eu/resource.html?uri=cellar:864f472b-34e9-11ed-9c68-01aa75ed71a1.0001.02/DOC_1&format=PDF}{proposal itself} (just skim it) and \href{https://eur-lex.europa.eu/resource.html?uri=cellar:864f472b-34e9-11ed-9c68-01aa75ed71a1.0001.02/DOC_2&format=PDF}{Annexes I, II, and III} in full
\end{itemize}

\section{}

Revisit your systems diagram from Homework 1, and answer the following questions (15 points):

\begin{enumerate}
    \item If every company in the US were to implement the NIST Cybersecurity Framework, would this affect your chosen system? Why or why not? 200 words max. 
    \item If the EU Cyber Resiliance Act is passed, how does this affect your chosen system? 200 words max.
    \item The White House's National Cybersecurity Strategy aims to disrupt negative feedback loops that prevent the adoption of good security practices. In your systems diagram, where (if at all) might the National Cybersecurity Strategy improve security outcomes? Point to specific nodes/vertices in your diagram if applicable. 200 words max.
\end{enumerate}



\end{document}
