\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}


\title{The Economics of Cybersecurity: Presentation \#3}
\author{}
\date{Due: In class April 23, 2024}


\begin{document}

\maketitle

Prepare a 10-minute presentation on a segment of the cybersecurity industry. Please pick a topic from the list provided \href{https://docs.google.com/spreadsheets/d/1SdaMpeCo4CE8o0U_irGhWmVXJYHybRWoiX4uwZYMhCE/edit#gid=2144152383}{here}. Please choose a different topic from your fellow classmates. 
\\
\\
You are free to structure your 10 minutes as you like. As a suggestion, some questions you may want to consider answering are:
\begin{itemize}
    \item What good or service does this market segment provide?
    \item What are the technical elements of these goods or services? How do they work?
    \item Who are the major companies or organizations in this segment? What are the differences between them? 
    \item Who are the customers? How much do they pay for this good or service? Why do they purchase this good or service?
    \item How much does this market segment earn in a year? Is this market segment growing? Shrinking? Stagnating?
    \item How long has this market segment existed? Consider giving a history of the subject.
    \item What are some of the challenges facing this market segment?
    \item What externalities (if any) does this market segment produce?
\end{itemize}

Some the above questions may not have clearly defined answers, and it is OK to engage in some degree of hypothesizing or speculation, but make it clear when doing so. Cite your sources liberally. 
Be prepared to answer 1--5 minutes of questions at the end of your presentation.


\subsection*{Grading}

You will be evaluated on the following:
\begin{enumerate}
    \item (20\%) Your ability to find the appropriate sources and evaluate their trustworthiness
    \item (20\%) Your ability to succinctly convey technical details to the audience
    \item (20\%) Your ability to comprehensively cover the subject material
    \item (20\%) Overall clarity
    \item (10\%) Your ability to answer questions from the audience
    \item (10\%) Your ability to ask insightful questions of other students' presentations
\end{enumerate}

If you plan on using slides, please share your slides with me before class.


\end{document}
